Video Doesn't Lie

### 2016-04-30 nyu-data-science-reproducibility-16/video-reproducibility.Rmd
Add better URL to talk repo
Embed more videos, iframes

---
title: "video-and-reproducible-science"
author: "Karen E. Adolph & Rick O. Gilmore"
date: "`r Sys.time()`"
output: 
  ioslides_presentation:
    widescreen: TRUE
    css: css/databrary.css
    logo: img/databrary-leaf-large.png
bibliography: bib/databrary.bib
---

@@

## “Video Doesn’t Lie"

<div class=centered>
**Reproducible Workflows With [Databrary](http://databrary.org)**

@@

<http://github.com/databrary/presentations/nyu-data-science-reproducibility-16/video-reproducibility>
</div>

@@

- Methodological details not captured in write-ups
- Unequivocally & unambiguously demonstrates phenomenon

## Children's Scale Errors

@@

## Children's Scale Errors {.vcenter}

@@

@@

- "Active" curation of data *as it's collected*
- Organize, share, standardize participant metadata
- Share materials, displays

@@

- External links to code repos
- DOIs for shared datasets
- Long-term preservation via partnership with NYU Libraries

## Scripting Video Data Analyses

@@

## Datavyu Script Example 1

- Checking/correcting errors

@@

- Video captures behavior
- Databrary securely stores, shares video
- Video + Databrary -> reproducible & transparent workflows
- Video + Datavyu -> reproducible & transparent workflows
- Databrary helps make psychological science more transparent & reproducible

>>>>

---
title: "Video Doesn't Lie"
author: "Karen E. Adolph, David Millman, and Rick O. Gilmore"
date: "`r Sys.time()`"
output: 
  ioslides_presentation:
    widescreen: TRUE
    css: css/databrary.css
    logo: img/databrary-leaf-large.png
bibliography: bib/databrary.bib
---

@@

----

<div class=centered>
**Video Doesn't Lie:**</br>
**Reproducible Workflows With [Databrary](http://databrary.org)**

@@

<http://github.com/databrary/presentations/nyu-data-science-reproducibility-16/>
</div>

@@

- Methodological details not captured in write-ups
- Unequivocally & unambiguously demonstrates phenomena

----

@@

----

@@

----

<iframe src="http://databrary.org" width=700px height=550px>
</iframe>

@@

- "Active" curation of data **as it's collected**
- Organize, share, standardized participant metadata

## [[@15586370-3088-4527-bd0e-88ec0d8d673c]](http://dx.doi.org/10.17910/B7WC7S)

<iframe src="https://nyu.databrary.org/volume/2" width=750px height=500px>
</iframe>

@@

- Share materials, displays
- External links to code repos
- DOIs for shared datasets
- Long-term preservation via partnership with NYU Libraries

## Getting Permission to Share

<div class="centered">
<video width="640" height="480" controls>
  <source src="https://databrary.org/video/example-video-1.mp4" type="video/mp4">
Your browser does not support the video tag.
</video>

<https://databrary.org/access/guide.html>
</div>

## Reproducible video coding workflows

@@

----

<div class="centered">
<video width="640" height="480" controls>
  <source src="http://datavyu.org/user-guide/_static/video/run-a-script.mp4" type="video/mp4">
Your browser does not support the video tag.
</video>
</div>

@@

- Video captures behavior
- Databrary securely stores, shares video
- Video + Databrary -> reproducible & transparent workflows

## Take homes

- Video + Datavyu -> reproducible & transparent workflows
- Databrary helps make psychological science more transparent & reproducible
